### 2020-07-27 CILAMCE_2020/paper.tex
Update data preparation section

\item The final number of samples has been reduced from 1030 rows to 916 rows, with 416 different ingredient configurations (IDs);

@@

@@

% --------------------------------------------------------------------------
% \subsection{Obtaining the data} \label{subsec:Obtainingthedata}
% --------------------------------------------------------------------------

% --------------------------------------------------------------------------
% \subsection{Data preparation} \label{subsec:datapreparation}
% --------------------------------------------------------------------------

% --------------------------------------------------------------------------
% \subsection{Data visualization} \label{subsec:datavisualization}
% --------------------------------------------------------------------------

% --------------------------------------------------------------------------
% \subsection{Machine learning models} \label{subsec:machinelearningmodels}
% --------------------------------------------------------------------------

>>>>

@@

After these manipulations, the final number of samples has been reduced from 1030 rows to 916 rows, with 416 different ingredient configurations (IDs). A xls file named "TODO" of the data at this point is available at the github repo (TODO: referencia bibliografica do link do arquivo no github, que tem o nome de "data\_2.xls", preciso fazer uma pasta com os arquivos e nomear de forma melhor no github - ainda vou fazer uma limpa no github e excluir muita coisa lá).

@@
